On Misuses of the Kolmogorov–Smirnov-Test

### 2022-04-22 Manuscript/manuscript.tex
updated conclusion

Conclusion here.

\citet{Butorina}
\citet{Racine}
\citet{Wang}

>>>>

The K-S test has base assumptions that the hypothesized distribution is completely specified
and the data is independent. When these assumptions are violated, the test is no
longer accurate and remedies must be performed. In the case of fitted parameters, 
parametric and non-parametric bootstrap can restore the power of the test. A bias 
correction is required if the non-parametric form is used \citep{Babu}. In the case of dependent
data, a procedure using bootstrap with copulas to model dependency shows positive results.
When both assumptions are violated, that is the case where the data has dependence and 
parameters must be fitted, the copula remedy also shows positive results. The tests were 
performed on simulated data from a standard normal distribution, though also appear effective
against other distributions such as gamma and gev. The copula remedy
is not a complete solution. Regardless of the true depedence, we use an AR(1) model.
Therefore, if the AR(1) model is a close approximation of the truth, the fix can work.
However, in cases such as AR(2), the approximation is incorrect and the fix does not 
completely restore power.
